Analysis

### 2020-03-20 production/prod_analysis-cfa.rmd
update20marzo

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = FALSE)
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = TRUE)
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```
